\title{Homework 1 - Group 34}
\author{
        Sean Caster,
        Joshua Sean Bell,
        Tarren Engberg
}
\date{April 15th, 2018}

\documentclass[titlepage]{article}
\usepackage{geometry}
\geometry{letterpaper, margin=0.75in}

\begin{document}
\maketitle

\begin{abstract}
Group 34's discussion of the process for running the Yocto version of Linux.
\end{abstract}

\section{Introduction}
Here is a spot for the intro.

\paragraph{Outline}

\begin{description}
  \item[$\bullet$] A log of commands used to perform the requested actions, as well as a write-up of your concurrency solution.
  \begin{description}
    \item[$\bullet$] Command 1
    \item[$\bullet$] Command 2
    \item[$\bullet$] Command 3
  \end{description}
  \item[$\bullet$] An explanation of each and every flag in the listed qemu command-line
  \begin{description}
    \item[$\bullet$] -gdb tcp:5534 allows qemu to be used with a debugger on port 5534
    \item[$\bullet$] -S keeps the CPU from running at startup
    \item[$\bullet$] -nographic disables qemu's graphical output
    \item[$\bullet$] -kernel tells qemu to use the given kernel image
    \item[$\bullet$] -drive defines a new drive
    \item[$\bullet$] -enable-kvm starts qemu in kernel virtual machine
    \item[$\bullet$] -net none tells qemu that no network devices should be configured
    \item[$\bullet$] -usb enables the USB driver
    \item[$\bullet$] -localtime to start at the current local time
    \item[$\bullet$] --no-reboot tells qemu to exit rather than rebooting
    \item[$\bullet$] -append indicates the command line to use
  \end{description}
  \item[$\bullet$] What do you think the main point of this assignment is?
  \item[$\bullet$] How did you personally approach the problem? Design decisions, algorithm, etc.
  \item[$\bullet$] How did you ensure your solution was correct? Testing details, for instance.
  \item[$\bullet$] What did you learn?
  \item[$\bullet$] Version control log (formatted as a table) -- there are any number of tools for generating a TeX table from repo logs
  \item[$\bullet$] Work log. What was done when? Be detailed.
\end{description}


\end{document}
